% Copyright 2019 Jake Besworth
%
% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at
%
%    http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing, software
% distributed under the License is distributed on an "AS IS" BASIS,
% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
% See the License for the specific language governing permissions and
% limitations under the License.


%% Extended Article for font-size
\documentclass[9pt]{extarticle}

%% Black and White vs Design
\newcommand*{\PRINT}{}

%% Font
\usepackage[T1]{fontenc}
% \usepackage{librebaskerville}
% \usepackage{kpfonts,baskervald}
\usepackage{ebgaramond}
\usepackage{fontawesome}
\usepackage[sfdefault]{FiraSans} %% option 'sfdefault' activates Fira Sans as the default text font
\usepackage[T1]{fontenc}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}

\makeatletter
\newcommand\HUGE{\@setfontsize\Huge{20pt}{24pt}}
\makeatother

%% Packages
\usepackage{color}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{scrextend}
\usepackage{tabto}
\usepackage[margin=1in]{geometry}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}

%% Page Indentation and Line Spacing
\setlength{\parskip}{10pt}
\setlength{\parindent}{0pt}
\linespread{1.12}
\pagenumbering{gobble}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.75in}

%% Custom Colours
\definecolor{linkblue}{RGB}{6,69,173}
\definecolor{darkgrey}{RGB}{68,68,68}
\definecolor{mediumgrey}{RGB}{102,102,102}

\ifdefined\PRINT
    \definecolor{em-light}{RGB}{0,0,0}
    \definecolor{lightgrey}{RGB}{221,221,221}
\else
    \definecolor{em-light}{RGB}{25,130,232}
    \definecolor{lightgrey}{RGB}{25,130,232}
\fi

%% Word Wrap
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\begin{document}

%%Begin%% Header
{
    \begin{tabularx}{\textwidth}{Xr}
    {\HUGE\leavevmode\color{em-light} Jake Besworth} &
        \null\hfill\small\begin{tabular}{llX}
            \faMapMarker\space\space\space\color{darkgrey} Toronto Ontario, Canada & \faEnvelope\space\space\color{darkgrey} \href{mailto:jake@besworth.io}{jake@besworth.io} \\[3px]
            \faGithub\space\space\color{darkgrey} \href{https://github.com/jakebesworth}{github.com/jakebesworth} & {\large\faMobilePhone}\space\space\space\color{darkgrey} +1 (000) 000 0000 \\[10px]
        \end{tabular}
    \end{tabularx}

    {\color{lightgrey}{\centerline{\rule{17cm}{0.4pt}}}}
}
%%End%% Header
%%Begin%% Body
{
    %%Begin%% Programming
    \begin{Large}
        \color{em-light}\textbf{\\[-5pt]{\firamedium Development Experience}\\}
    \end{Large}

    \begin{tabularx}{\textwidth}{llX}
    \faHtml5\space\space{\bfseries {\firamedium Front-end}}         & {\color{darkgrey} \textbullet\space\space Vue.js (Vuex, Vue Router, PWA), SASS, Vuetify, Webpack, Mocha \& Karma tests} & \\[5pt]
                                                                    & {\color{darkgrey} \textbullet\space\space React (Redux, Router), Bootstrap 3 \& 4, Backbone, Angular, jQuery, Jest tests} & \\[12pt]
    \faDatabase\space\space{\bfseries {\firamedium Back-end}}       & {\color{darkgrey} \textbullet\space\space Python 2 \& 3, Django, Flask, SQLAlchemy} & \\[5pt]
                                                                    & {\color{darkgrey} \textbullet\space\space Ruby, Ruby on Rails, Prawn} & \\[5pt]
                                                                    & {\color{darkgrey} \textbullet\space\space PHP 5 \& 7, Slim 3, WordPress, Symphony} & \\[5pt]
                                                                    & {\color{darkgrey} \textbullet\space\space Java 8, Spring, Hibernate, JPA, JasperReports, Log4, Apache Tomcat \& Maven} & \\[5pt]
                                                                    & {\color{darkgrey} \textbullet\space\space Relational Databases (MySQL \& MariaDB, PostgreSQL, Informix), Redis, Cloud Datastore} & \\[12pt]
    \faLinux\space\space{\bfseries {\firamedium Environment}}       & {\color{darkgrey} \textbullet\space\space GNU/Linux (Alpine, CentOS, RHEL), Google Cloud Platform (GKE, GCF), AWS, Digital Ocean} & \\[5pt]
                                                                    & {\color{darkgrey} \textbullet\space\space Git, SVN, Bash, Apache, NGINX, Docker, Kubernetes, Make, Node.js} & \\[12pt]
    \end{tabularx}
    %%End%% Programming
    %%Begin%% Experience
    {\color{lightgrey}{\centerline{\rule{17cm}{0.4pt}}}}
    \begin{Large}
        \color{em-light}\textbf{\\[5pt]{\firamedium Work Experience}\\[-5pt]}
    \end{Large}

    \textbf{{\firamedium Software Developer at \textit{Tulip Retail}}}{\color{darkgrey}\hfill{\small{May 2018 to Present\\[5pt]}}
        Software Developer on the Innovation team, working on proof of concepts, developing software, and technically leading partnerships (Salesforce, Shopify). Tech lead of the Salesforce service \& marketing cloud connectors architecting and using Vue.js, Node.js (async/await), ETL, Google Cloud Functions. Worked on transition from monolith projects to serverless, microservices, and Saas webhooks.
    }

    \textbf{{\firamedium Undergraduate Teaching Assistant at the \textit{University of Guelph}}}{\color{darkgrey}\hfill{\small{January 2018 to April 2018}}
    }

    \textbf{{\firamedium Software Engineer (Co-op) at \textit{Wave}}}{\color{darkgrey}\hfill{\small{May 2017 to August 2017\\[5pt]}}
        Full stack developer on the Accounting team, in Toronto Canada. Worked on the \textit{Next Accounting} software, using Python, Django, React, Docker, and created a highly scalable PDF report generation service, using Ruby on Rails \& Prawn. Developed A/B testing, and analytics for other projects.\\
    }

    \textbf{{\firamedium Full Stack Developer (Co-op) at \textit{Tulip Retail}}}{\color{darkgrey}\hfill{\small{January 2017 to April 2017\\[5pt]}}
        Full stack web developer on the \textit{Well.ca} team, in Toronto Canada. Worked on front-end design, as well as back-end feature additions, and bug fixes mostly with PHP5 and various other technologies. \\
    }

    \textbf{{\firamedium Web Developer (Co-op) at \textit{Symcor Inc.}}}{\color{darkgrey}\hfill{\small{May 2016 to August 2016\\[5pt]}}
        Full stack developer on the Enterprise Architecture team. Worked with a full Java stack doing feature implementation on a complex web application that collected data on all software at Symcor. \\
    }
    %%End%% Experience
    %%Begin%% Education
    {\color{lightgrey}{\centerline{\rule{17cm}{0.4pt}}}}
    \begin{Large}
        \color{em-light}\textbf{\\[-5pt]{\firamedium Education}\\[-5pt]}
    \end{Large}

    \textit{\textbf{{\firamedium University of Guelph}}}{\color{darkgrey}{\hfill{\small{Graduated 2018\\[5pt]}}
    Bachelor of Computing, Software Engineering (Co-op)}}
    %%End%% Education
}
%%End%% Body
\end{document}